\newenvironment{features}{\begin{description}}{\end{description}}
\newcommand\feat{\item[]}

\clearpage

\section{Features in Scope}

\subsection{Model Definition}

\pharmml can encode in a model:
\begin{features}
\feat Arbitrary level of variability, both levels lower and higher than between subject variability.
\feat Continuous covariates.
\feat Categorical covariates.
\feat Population parameters.
\feat Parameters with multiple levels of variability.
\feat Covariates related to parameters using a linear model.
\feat Parameters and covariates can be sampled from a probability distribution.
\feat The covariance matrix for each level of variability, typically $\Omega$ for between subject variability.
\feat A structural model defined as an algebraic expression.
\feat A structural model defined as a system of ODEs, with initial conditions.
\feat A structural model that is defined as an SBML model.
\feat A continuous observation model:a residual error model applied to one or more variables in the structural model.
\end{features}


\subsection{Trial Design}

\pharmml can encode these features in a trial design:
\begin{features}
\feat Bolus dosing
\feat Infusion dosing
\feat Multiple dosing regimens including mixed bolus and infusion
\feat Repeated dosing
\feat Dosing at arbitrary time points
\feat Steady state dosing
\feat Dosing to more than one compartment
\feat Cross-over studies
\feat Parallel design
\feat Washout periods
\feat Run-in periods
\feat Inter-occasion variability
\feat Between Subject Variability
\end{features}

\subsection{Modelling Steps}

\pharmml can encode these features when describing the execution of a model:
\begin{features}
\feat Simulation of a model using the trial design described in \pharmml.
\feat Simulation using the trial design described in data file.
\feat The definition of a continuous variable to be observed and the time-points of observation.
\feat Estimation of a model using the trial design described in \pharmml and objective data encoded in a data file.
\feat Estimation of a model using the trial design and objective data encoded in a data file.
\end{features}

\section{Feature out of Scope}

\subsection{Model Definition}

\pharmml cannot encode:
\begin{features}
\feat Conditional continuous covariates.
\feat Discrete observation models.
\feat Bayesian models.
\end{features}


\subsubsection{Trial Design}

\pharmml cannot encode these features in a trial design:
\begin{features}
\feat Trials with different centres or other levels of organisation above study groups (aka arms)
\feat Levels of variability below one level of inter-occasion variability.
\end{features}

\subsection{Modelling Steps}

\pharmml cannot encode these features when describing the execution of a model:
\begin{features}
\feat The export of simulation results to an external file.
\feat  The export of estimation results to an external file.
\feat Transfer of results from one modelling step to another, for example transferring estimation results to a simulation step.
\end{features}
